### 2015-04-17 abstract2.tex
Checking 1
Checking paper 1

In this dissertation, I will discuss and research about Lifschitz and Turner’s splitting set and program splitting theorem. The main achievements obtained in this dissertation are shown as following details.

Firstly, I extend Lifschitz and Turner’s splitting set and program splitting theorem to allow the program to be split by an arbitrary set of atoms and introduce a new program splitting method for NLP. After this, I extend this result to DLP and propose the strong splitting method. As the splitting set can be an arbitrary set of atoms, the applicability of program splitting can be extended greatly.

@@

Thirdly, during analyzing how the new splitting set effect on the performance of new splitting method, I found out that if atoms in the splitting set are satisfied by every answer set of the program, it could release the computational complexity of answer set solving. According to this, this dissertation extends the usage of splitting set to program simplification. In the same words, we can use consequence of the ASP programs to simplify themselves. The consequence of an ASP program is a set of literals that are satisfied by every answer set of the program. I take only positive literals to make them as atoms. The purpose of program simplification is still to speed up solving answer sets of ASP program.

>>>>

This dissertation will discuss and research about Lifschitz and Turner's splitting set and program splitting theorem. The main achievements obtained in this dissertation are shown as following details.

Firstly, this dissertation extends Lifschitz and Turner's splitting set and program splitting theorem to allow the program to be split by an arbitrary set of atoms and introduce a new program splitting method for NLP. After this, this dissertation extend this result to DLP and propose the strong splitting method. As the splitting set can be an arbitrary set of atoms, the applicability of program splitting can be extended greatly.

@@

Thirdly, during analyzing how the new splitting set effect on the performance of new splitting method, dissertation found out that if atoms in the splitting set are satisfied by every answer set of the program, it could release the computational complexity of answer set solving. According to this, this dissertation extends the usage of splitting set to program simplification. In the same words, we can use consequence of the ASP programs to simplify themselves. 
%The consequence of an ASP program is a set of literals that are satisfied by every answer set of the program. I take only positive literals to make them as atoms.
The purpose of program simplification is still to speed up solving answer sets of ASP program.
